\documentclass[a4paper, 12pt]{article}
\begin{document}
\title{Project Proposition: Computer Science Forum}
\author{Group No. 2}
\maketitle


	\section{Problem/Opportunity}

	Currently, a platform suitable for discussion of 
	computer science coursework is conspicuously missing. 
	If a student is confused about an assignment, they may 
	contact the tutor or the professor, or their course friends. 
	However, some students may be too shy to e-mail a professor or a 
	tutor, and may be unfortunately friendless. In such a case, 
	the student will find themselves in a rather precarious position.
 
	
	Thus, a casual and accessible platform for discussion of coursework is needed.


	%-------------------------------------------------------------

	\section{Proposition}

	 A forum, exclusive to students enrolled in courses affiliated with the School of Computer Science could be built.


	 Such a forum would feature sections split by 
	 years, as well as by modules, where relevant 
	 information about said modules could be discussed 
	 and collected by the students. The forum would be freely 
	 accessible by students and lecturers alike, such that 
	 full transparency is guaranteed, and indeed the 
	 lecturers themselves could contribute to the posts.


	 The forum could be expanded to contain things such as stickied posts, 
	 which could contain currently due assignments and their specifications, 
	 sections for discussion of courses overall, surveys which 
	 would be presented to registered users et cetera.


	%-------------------------------------------------------------
	
	\newpage

	\section{Value}

	The forum usefulness is too large to describe for the average student. 
	If someone is confused about a piece of coursework, but do not want to 
	make a fool of themselves, the forum would serve their needs nicely. 
	If a lecturer is fond of using the blackboard, and a student misses a 
	lecture, they would be able to ask their fellow classmates for a possible 
	copy of the written notes in photographic form. Sticky posts would act 
	as a useful summary of currently due coursework and common useful 
	information about the course (for instance, book such and such is a must read etc.).

	Similarly, the lecturers would find the forum useful as a source of unbiased and genuine 
	feedback on their courses, since any problems are present are bound to come 
	up in the forums. Surveys could also be designed etc.

	%-------------------------------------------------------------

	\section{Conclusion}

	It appears to us that a forum designed for the needs of 
	the Computer Science students here at TCD would improve 
	the course in a significant way, making the coursework more accessible, 
	promoting student collaboration and teamwork, as well as 
	providing a source of feedback for the lecturers.

\end{document}
