\documentclass[a4paper, 12pt]{article}
\usepackage{enumitem}

\begin{document}
\title{Week 2 Minutes}
\author{Group No. 2}
\maketitle

	\section{Attendance:}
		\begin{enumerate}[label*=\arabic*.]
			\item Andrius Buinovskij:	\dotfill Present
			\item Conor McKenna:		\dotfill Present
			\item Jerico Alcaras		\dotfill Present
			\item Joseph Fitzpatrick	\dotfill Present
			\item Liam Farrelly		\dotfill Present
			\item Laura Young		\dotfill Present
		\end{enumerate}

	\section{Agenda:}
		\begin{enumerate}[label*=\arabic*.]
			\item Decide on front-end and back-end roles for the team.
			\begin{enumerate}[label*=\arabic*.]
				\item Conor and Andrew: Back-end - SQL.
				\item Jerico, Joseph, Laura and Liam: Front-End - As of yet undecided.
			\end{enumerate}	
			\item Proposed ideas for front end language to be voted upon by the front-end team are:
			Javascript, Java, Ruby, D, HTML/CSS, PHP.
			\item Decided group leader: Andrius Buinovskij.
			\item Proposed features for implementation in the forum.
			\begin{enumerate}[label*=\arabic*.]
				\item Highlighting best response to question.
				\item User run polls.
				\item Text editing support (e.g. code boxes).
			\end{enumerate}
		\end{enumerate}

	\section{Assigned tasks:}
		\begin{enumerate}[label*=\arabic*.]
			\item Spend time researching different languages to use in implementing front-end of the project.
			\item Provide learning and research resources for the languages suggested.
			\item Set up a Github repository for the group.
		\end{enumerate}

	\section{Date and location of next meeting:}
		15:00, February 1st, Glass Rooms.

\end{document}
