\documentclass[a4paper, 12pt]{article}
\usepackage{enumitem}

\begin{document}
\title{Week 9 Minutes}
\author{Group No. 2}
\date{March 14, 2016}
\maketitle

	\section{Attendance:}
		\begin{enumerate}[label*=\arabic*.]
			\item Andrius Buinovskij:	\dotfill Present
			\item Conor McKenna:		\dotfill Present
			\item Jerico Alcaras		\dotfill Present
			\item Joseph Fitzpatrick	\dotfill Abent
			\item Liam Farrelly		\dotfill Present
			\item Laura Young		\dotfill Present
		\end{enumerate}

	\section{Agenda:}
		\begin{enumerate}[label*=\arabic*.]
			\item Lecturer/Moderator verification process.
				\begin{enumerate}[label*=\arabic*.]
					\item Problem arises since student and lecturer tcd e-mails are indistiguishable.
					\item The solution is to manually give lecturers moderator privileges.
				\end{enumerate}
			\item SSH'ing and the KDEG server.
				\begin{enumerate}[label*=\arabic*.]
					\item A quick tutorial was given on how to access the KDEG servers.
				\end{enumerate}
			\item Status update.
				\begin{enumerate}[label*=\arabic*.]
					\item Database complete.
					\item Signup system is written, yet to be tested.
					\item Login system complete.
					\item Displaying data from back end complete.
				\end{enumerate}
		\end{enumerate}

	\newpage
	\section{Assigned tasks:}
		\begin{enumerate}[label*=\arabic*.]
			\item Tasks for front end team.
			\begin{enumerate}[label*=\arabic*.]
				\item Display the rest of data as it is stored in the database.
				\item Data entry.
				\item User profiles and permissions.
				\item Set up apache server.
				\item Research WOMP, Xampp.
			\end{enumerate}
		\end{enumerate}

	\section{Date and location of next meeting:}
		15:00, March 21st, Glass Rooms.

\end{document}
