\documentclass[a4paper, 12pt]{article}
\usepackage{enumitem}

\begin{document}
\title{Week 4 Minutes}
\author{Group No. 2 - Screw you Gary, we'll call it what we want.}
\date{February 8, 2016}
\maketitle

	\section{Attendance:}
		\begin{enumerate}[label*=\arabic*.]
			\item Andrius Buinovskij:	\dotfill Present
			\item Conor McKenna:		\dotfill Present
			\item Jerico Alcaras		\dotfill Present
			\item Joseph Fitzpatrick	\dotfill Present
			\item Liam Farrelly		\dotfill Present
			\item Laura Young		\dotfill Present
		\end{enumerate}

	\section{Agenda:}
		\begin{enumerate}[label*=\arabic*.]
			\item Members are sufficiently proficient in HTML to begin working.
			\begin{enumerate}[label*=\arabic*.]
				\item Will also study PHP.
			\end{enumerate}
			\item Decided on moderator functionality
			\begin{enumerate}[label*=\arabic*.]
				\item Deletion and editing of posts and threads.
				\item Contain moderation tools within thread view.
			\end{enumerate}
		\end{enumerate}

	\newpage
	\section{Assigned tasks:}
		\begin{enumerate}[label*=\arabic*.]
			\item Tasks for front end team.
			\begin{enumerate}[label*=\arabic*.]
				\item Headers and footers - as a team.
				\item Supply database requirements to back end team - as a team.
				\item Log in screen - Laura.
				\item Home page - Joseph.
				\item Year group page - Liam.
				\item Sub-year modules - Jerico
			\end{enumerate}
			\item Tasks for back end team.
			\begin{enumerate}[label*=\arabic*.]
				\item Prepare requirements document.
				\item Design back-end SQL database.
			\end{enumerate}
		\end{enumerate}

	\section{Date and location of next meeting:}
		15:00, February 15th, Glass Rooms.

\end{document}
